### 2023-10-17 manuscript.tex
Add DOI from PLOS ONE [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/348c49975dcc5d8f29a226f04aaca4c476c8c667.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/348c49975dcc5d8f29a226f04aaca4c476c8c667/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/6547562661

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...c89de3aab786e55c724102ed14dbb33fb23561e5\#files_bucket}{is further updated} since re-submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/c89de3aab786e55c724102ed14dbb33fb23561e5/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/c89de3aab786e55c724102ed14dbb33fb23561e5}{habi/EAWAG-manuscript@c89de3a}
on September 14, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{OpenSCAD. {[}cited 14 Sep 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+3.gc52eec3.dirty documentation. {[}cited 14 Sep 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 14 Sep 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}

>>>>

\emph{A DOI-citable version of this manuscript is available at \url{https://doi.org/10.1371/journal.pone.0291003}}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/348c49975dcc5d8f29a226f04aaca4c476c8c667/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/348c49975dcc5d8f29a226f04aaca4c476c8c667}{habi/EAWAG-manuscript@348c499}
on October 17, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{OpenSCAD. {[}cited 17 Oct 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+3.gc52eec3.dirty documentation. {[}cited 17 Oct 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 17 Oct 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
